### 2011-06-23 docs/SDC/sdc.tex
typo
use maestrosymbols.tex

Maestro integrates the following system of equations:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& 
    -\nabla\cdot(\rho X_k\Ub) + \rho\omegadot_k,\label{eq:species}\\
\frac{\partial\Ub}{\partial t} &=& 
    -\Ub\cdot\nabla\Ub  - \frac{1}{\rho}\nabla\pi 
    - \frac{\rho-\rho_0}{\rho} g\eb_r,\label{eq:momentum}\\
\frac{\partial(\rho h)}{\partial t} &=& 
    -\nabla\cdot(\rho h\Ub) + \frac{Dp_0}{Dt} 
    + \rho\Hnuc ,\label{eq:enthalpy}
\end{eqnarray}
together with a constraint equation.

@@

In the Strang-split version of MAESTRO, the reaction and diffusion
processes operate independent of one-another.  The species and
enthalpy equations are updated through $\Delta t$ using the following
sequence:

@@

In the Strang-split version of Maestro, the reaction network solves just
the reaction portion of the species evolution equations along with a
temperature evolution equation.  This is done using a standard ODE solver
(like {\tt VODE}) on the system:
\begin{eqnarray}
\frac{dX_k}{dt} &=& \omegadot_k(\rho,X_k,T) \\
\frac{dT}{dt}   &=& 
    \frac{1}{c_p} \left ( -\sum_k \xi_k  \omegadot_k  + \Hnuc \right ).
\end{eqnarray}
Here, $T$ is evolved solely to evaluate the reaction rates,
$\omegadot_k(\rho,X_k,T)$.  Furthermore, we simplify the problem
``freezing'' the thermodynamics---i.e., $c_p$ is evaluating at the
start of the integration and held constant thereafter.

@@

\subsection{SDC version}
In the SDC version, the VODE integration at the end of an SDC
iteration is responsible for updating all the thermodynamic quantities
\{$\rho$, $(\rho h)$, and $(\rho X_k$)\}, including both the advective
fluxes (incorporated via a piecewise constant advective flux source
term) and the reactions.  This provides a much stronger coupling between
the physical processes.  In particular, our system now looks like:
\begin{eqnarray}
\frac{d(\rho X_k)}{dt} &=& \rho \omegadot_k(\rho,X_k,T) + A_{\rho X_k} \\
\frac{d(\rho h)}{dt}   &=& \rho \Hnuc + A_{\rho h}
\end{eqnarray}
Here, $A_{\rho X_k}$ and $A_{\rho h}$ are piecewise-constant (in time)
approximations to the change in ${\rho X_k}$ and ${\rho h}$ (respectively)
due to the advection.  These are constructed by calling {\tt density\_advance}
and {\tt enthalpy\_advance} in Maestro and passed into the network solver
during the reaction step.  These terms approximate the following:
\begin{eqnarray}
A_{\rho X_k} &=&  \left [- \nabla \cdot (\rho X_k \Ub) \right ]^{n+1/2} \\
A_{\rho h}   &=&  \left [- \nabla \cdot (\rho h U) + \frac{Dp_0}{Dt} \right ]^{n+1/2}
\end{eqnarray}
The construction of the interface states used in the advective terms
uses an iteratively-lagged approximation to the reaction source terms
in the interface prediction.  This explicitly couples the reaction
process to the advection process.

>>>>

\maestro\ integrates the following system of equations:
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& 
    -\nabla\cdot(\rho X_k\Ub) + \rho\omegadot_k,\label{eq:species}\\
\frac{\partial\Ub}{\partial t} &=& 
    -\Ub\cdot\nabla\Ub  - \frac{1}{\rho}\nabla\pi 
    - \frac{\rho-\rho_0}{\rho} g\eb_r,\label{eq:momentum}\\
\frac{\partial(\rho h)}{\partial t} &=& 
    -\nabla\cdot(\rho h\Ub) + \frac{Dp_0}{Dt} 
    + \rho\Hnuc ,\label{eq:enthalpy}
\end{eqnarray}
together with a constraint equation.

@@

In the Strang-split version of \maestro, the reaction and advection
processes operate independent of one-another.  The species and
enthalpy equations are updated through $\Delta t$ using the following
sequence:

@@

In the Strang-split version of \maestro, the reaction network solves just
the reaction portion of the species evolution equations along with a
temperature evolution equation.  This is done using a standard ODE solver
(like {\tt VODE}) on the system:
\begin{eqnarray}
\frac{dX_k}{dt} &=& \omegadot_k(\rho,X_k,T) \\
\frac{dT}{dt}   &=& 
    \frac{1}{c_p} \left ( -\sum_k \xi_k  \omegadot_k  + \Hnuc \right ).
\end{eqnarray}
Here, $T$ is evolved solely to evaluate the reaction rates,
$\omegadot_k(\rho,X_k,T)$.  Furthermore, we simplify the problem
``freezing'' the thermodynamics---i.e., $c_p$ is evaluating at the
start of the integration and held constant thereafter.

@@

\subsection{SDC version}
In the SDC version, the VODE integration at the end of an SDC
iteration is responsible for updating all the thermodynamic quantities
\{$\rho$, $(\rho h)$, and $(\rho X_k$)\}, including both the advective
fluxes (incorporated via a piecewise constant advective flux source
term) and the reactions.  This provides a much stronger coupling between
the physical processes.  In particular, our system now looks like:
\begin{eqnarray}
\frac{d(\rho X_k)}{dt} &=& \rho \omegadot_k(\rho,X_k,T) + A_{\rho X_k} \\
\frac{d(\rho h)}{dt}   &=& \rho \Hnuc + A_{\rho h}
\end{eqnarray}
Here, $A_{\rho X_k}$ and $A_{\rho h}$ are piecewise-constant (in time)
approximations to the change in ${\rho X_k}$ and ${\rho h}$ (respectively)
due to the advection.  These are constructed by calling {\tt density\_advance}
and {\tt enthalpy\_advance} in \maestro\ and passed into the network solver
during the reaction step.  These terms approximate the following:
\begin{eqnarray}
A_{\rho X_k} &=&  \left [- \nabla \cdot (\rho X_k \Ub) \right ]^{n+1/2} \\
A_{\rho h}   &=&  \left [- \nabla \cdot (\rho h U) + \frac{Dp_0}{Dt} \right ]^{n+1/2}
\end{eqnarray}
The construction of the interface states used in the advective terms
uses an iteratively-lagged approximation to the reaction source terms
in the interface prediction.  This explicitly couples the reaction
process to the advection process.

### 2011-06-23 docs/managing_jobs/managingjobs.tex
use maestrosymbols.tex

The submission script {\tt jaguar.run} and shell script
{\tt process.jaguar} in {\tt wdconvect/job\_scripts/}
are designed to allow you to run MAESTRO with minimal interaction,
while being assured that the data is archived to HPSS on the NCCS
machines.

>>>>

The submission script {\tt jaguar.run} and shell script
{\tt process.jaguar} in {\tt wdconvect/job\_scripts/}
are designed to allow you to run \maestro\ with minimal interaction,
while being assured that the data is archived to HPSS on the NCCS
machines.

### 2011-06-23 docs/pert_notes/pert.tex
use maestrosymbols.tex

The full density evolution equation is
\begin{eqnarray}
\frac{\partial\rho}{\partial t} &=& -\nabla\cdot(\rho\Ub) \nonumber \\
&=& -\Ub\cdot\nabla\rho - \rho\nabla\cdot\Ub \, . \label{rho equation}
\end{eqnarray}
The species are evolved according to
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& -\nabla\cdot(\rho\Ub X_k) + \rho \omegadot_k \nonumber \\
&=& -\Ub\cdot\nabla(\rho X_k) - \rho X_k \nabla\cdot\Ub + \rho \omegadot_k \, . \label{species equation}
\end{eqnarray}
In practice, only the species evolution equation is evolved, and the
total density is set as
\begin{equation}
\rho = \sum_k (\rho X_k)
\end{equation}
To advance $(\rho X_k)$ to the next timestep, we need to predict a
time-centered, interface state.  Algebraically, there are multiple
paths to get this interface state---we can predict $(\rho X)$ to the
edges as a single quantity, or predict $\rho$ and $X$ separately
(either in full or perturbation form).  In the notes below, we use the
subscript `{\tt edge}' to indicate what quantity was {\em predicted} to the
edges.  In MAESTRO, the different methods of computing $(\rho X)$ on
edges are controlled by the {\tt species\_pred\_type} parameter.  The
quantities predicted to edges and the 
resulting edge state are shown in the table~\ref{table:pred:species}

@@

We note that in essence these choices reflect a hyperbolic (1)
vs.\ elliptic (2) approach.  In MAESTRO, if we setup a problem with
$\rho = \rho_0$ initially, and enforce a constraint $\nabla \cdot
(\rho_0 \Ub) = 0$ (i.e.\ the anelastic constraint), then analytically,
we should never generate a $\rho'$.  To realize this behavior
numerically, we use $\rho_0^{n+\myhalf,{\rm avg}}$ in the prediction
of $(\rho X_k)$ on the edges to be consistent with the use of the
average of $\rho$ to the interfaces in the projection step at the end
of the algorithm.

@@

Maestro solves an enthalpy equation.  
The full enthalpy equation is
\begin{eqnarray}
\frac{\partial(\rho h)}{\partial t} &=& -\nabla\cdot(\rho h \Ub) + \frac{Dp_0}{Dt} 
+ \nabla\cdot \kth \nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext} \nonumber \\
&=& \underbrace{-\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub}_{-\nabla\cdot(\rho h\Ub)} 
+ \underbrace{\psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r}}_{\frac{Dp_0}{Dt}} 
+ \nabla\cdot\kth\nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext}.
\end{eqnarray}
%The full temperature equation is
%\begin{equation}
%\frac{\partial T}{\partial t} = -\Ub\cdot\nabla T
%+ \frac{1}{\rho c_p}\left\{(1-\rho h_p)\left[\psi
%+ (\Ubt \cdot \er )\frac{\partial p_0}{\partial r}\right] - \sum_k\rho\xi_k\dot\omega_k 
%+ \rho H_{\rm nuc} + \rho H_{\rm ext}\right\}.
%\end{equation}
Due to Strang-splitting of the reactions,the call to {\tt
  react\_state} has already been made.  Hence, the goal is to compute
an edge state enthalpy starting from $(\rho h)^{(1)}$ using an
enthalpy equation that does not include the $\rho H_{\rm nuc}$ and
$\rho H_{\rm ext}$ terms, where were already accounted for in {\tt
  react\_state}, so our equation becomes
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = -\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub 
+ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} + \nabla\cdot\kth\nabla T. \label{rhoh equation}
\end{equation}
We define the base state enthalpy evolution equation as
\begin{eqnarray}
\frac{\partial(\rho h)_0}{\partial t} &=& -\nabla\cdot[(\rho h)_0 w_0\eb_r] 
+ \frac{D_0p_0}{Dt} \nonumber \\
&=& -w_0\frac{\partial(\rho h)_0}{\partial r} 
- \underbrace{(\rho h)_0\frac{\partial w_0}{\partial r}+ \psi}_{``(\rho h)_0 ~ \text{force}"}
\enskip .\label{rhoh0 equation}
\end{eqnarray}

>>>>

The full density evolution equation is
\begin{eqnarray}
\frac{\partial\rho}{\partial t} &=& -\nabla\cdot(\rho\Ub) \nonumber \\
&=& -\Ub\cdot\nabla\rho - \rho\nabla\cdot\Ub \, . \label{rho equation}
\end{eqnarray}
The species are evolved according to
\begin{eqnarray}
\frac{\partial(\rho X_k)}{\partial t} &=& -\nabla\cdot(\rho\Ub X_k) + \rho \omegadot_k \nonumber \\
&=& -\Ub\cdot\nabla(\rho X_k) - \rho X_k \nabla\cdot\Ub + \rho \omegadot_k \, . \label{species equation}
\end{eqnarray}
In practice, only the species evolution equation is evolved, and the
total density is set as
\begin{equation}
\rho = \sum_k (\rho X_k)
\end{equation}
To advance $(\rho X_k)$ to the next timestep, we need to predict a
time-centered, interface state.  Algebraically, there are multiple
paths to get this interface state---we can predict $(\rho X)$ to the
edges as a single quantity, or predict $\rho$ and $X$ separately
(either in full or perturbation form).  In the notes below, we use the
subscript `{\tt edge}' to indicate what quantity was {\em predicted} to the
edges.  In \maestro, the different methods of computing $(\rho X)$ on
edges are controlled by the {\tt species\_pred\_type} parameter.  The
quantities predicted to edges and the 
resulting edge state are shown in the table~\ref{table:pred:species}

@@

We note that in essence these choices reflect a hyperbolic (1)
vs.\ elliptic (2) approach.  In \maestro, if we setup a problem with
$\rho = \rho_0$ initially, and enforce a constraint $\nabla \cdot
(\rho_0 \Ub) = 0$ (i.e.\ the anelastic constraint), then analytically,
we should never generate a $\rho'$.  To realize this behavior
numerically, we use $\rho_0^{n+\myhalf,{\rm avg}}$ in the prediction
of $(\rho X_k)$ on the edges to be consistent with the use of the
average of $\rho$ to the interfaces in the projection step at the end
of the algorithm.

@@

\maestro\ solves an enthalpy equation.  
The full enthalpy equation is
\begin{eqnarray}
\frac{\partial(\rho h)}{\partial t} &=& -\nabla\cdot(\rho h \Ub) + \frac{Dp_0}{Dt} 
+ \nabla\cdot \kth \nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext} \nonumber \\
&=& \underbrace{-\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub}_{-\nabla\cdot(\rho h\Ub)} 
+ \underbrace{\psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r}}_{\frac{Dp_0}{Dt}} 
+ \nabla\cdot\kth\nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext}.
\end{eqnarray}
%The full temperature equation is
%\begin{equation}
%\frac{\partial T}{\partial t} = -\Ub\cdot\nabla T
%+ \frac{1}{\rho c_p}\left\{(1-\rho h_p)\left[\psi
%+ (\Ubt \cdot \er )\frac{\partial p_0}{\partial r}\right] - \sum_k\rho\xi_k\dot\omega_k 
%+ \rho H_{\rm nuc} + \rho H_{\rm ext}\right\}.
%\end{equation}
Due to Strang-splitting of the reactions,the call to {\tt
  react\_state} has already been made.  Hence, the goal is to compute
an edge state enthalpy starting from $(\rho h)^{(1)}$ using an
enthalpy equation that does not include the $\rho H_{\rm nuc}$ and
$\rho H_{\rm ext}$ terms, where were already accounted for in {\tt
  react\_state}, so our equation becomes
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = -\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub 
+ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} + \nabla\cdot\kth\nabla T. \label{rhoh equation}
\end{equation}
We define the base state enthalpy evolution equation as
\begin{eqnarray}
\frac{\partial(\rho h)_0}{\partial t} &=& -\nabla\cdot[(\rho h)_0 w_0\eb_r] 
+ \frac{D_0p_0}{Dt} \nonumber \\
&=& -w_0\frac{\partial(\rho h)_0}{\partial r} 
- \underbrace{(\rho h)_0\frac{\partial w_0}{\partial r}+ \psi}_{``(\rho h)_0 ~ \text{force}"}
\enskip .\label{rhoh0 equation}
\end{eqnarray}

### 2011-06-23 docs/preface/preface.tex
use maestrosymbols.tex

MAESTRO is developed at the Center for Computational Sciences and
Engineering at Lawrence Berkeley National Laboratory and at Stony
Brook University.  Development was supported by the SciDAC Program of
the DOE Office of Mathematics, Information, and Computational Sciences
and the SciDAC Program of the DOE Office of High Energy Physics under
the U.S. Department of Energy under contract No.\ DE-AC02-05CH11231 to
LBNL and by a DOE/Office of Nuclear Physics grant No.\
DE-FG02-06ER41448, to Stony Brook. \\

\noindent The current version of the MAESTRO User's Guide can be found in 
the MAESTRO source tree under {\tt fParallel/MAESTRO/docs/}.

>>>>

This documentation is a work in progress.  \maestro\ is rapidly
evolving, so portions of the text are likely to be incomplete or
out-of-date. \\

\noindent \maestro\ is developed at the Center for Computational Sciences and
Engineering at Lawrence Berkeley National Laboratory and at Stony
Brook University.  Development was supported by the SciDAC Program of
the DOE Office of Mathematics, Information, and Computational Sciences
and the SciDAC Program of the DOE Office of High Energy Physics under
the U.S. Department of Energy under contract No.\ DE-AC02-05CH11231 to
LBNL and by a DOE/Office of Nuclear Physics grant No.\
DE-FG02-06ER41448, to Stony Brook. \\

\noindent The current version of the \maestro\ User's Guide can be found in 
the \maestro\ source tree under {\tt fParallel/MAESTRO/docs/}.

### 2011-06-23 docs/visualization/visualization.tex
add the visualization chapter
use maestrosymbols.tex

\section{Visualizing with \amrvis}
\section{Visualizing with \visit}
\section{Visualizing with \yt}
\yt is a Python package for analyzing and visualizing simulation data.
Originally \yt was written for the {\tt Enzo} code, with focus on
cosmological simulation data.  It has since been refactored to remove
the specific {\tt Enzo}isms, and now can work on various data formats,
such as the BoxLib data from {\tt MAESTRO} and {\tt CASTRO}, HDF5 data
from {\tt FLASH}, and data from the SPH code {\tt Gadget}.  For more
information, see the \yt homepage at {\tt http://yt.enzotools.org/}.

@@

\begin{figure}[!h]\label{fig:yt_slice}
\centering
\includegraphics[height=0.4\textheight]{my_cool_images_Slice_x_tfromp_trim}
\caption{Example slice through 3-d dataset with \yt.}
\end{figure}

>>>>

\section{Visualizing with \amrvis}
\section{Visualizing with \visit}
\section{Visualizing with \yt}
\yt is a Python package for analyzing and visualizing simulation data.
Originally \yt was written for the {\tt Enzo} code, with focus on
cosmological simulation data.  It has since been refactored to remove
the specific {\tt Enzo}isms, and now can work on various data formats,
such as the BoxLib data from \maestro\ and \castro, HDF5 data
from {\tt FLASH}, and data from the SPH code {\tt Gadget}.  For more
information, see the \yt homepage at {\tt http://yt.enzotools.org/}.

@@

\begin{figure}[!h]\label{fig:yt_slice}
\centering
\includegraphics[height=0.4\textheight]{\visfigpath/my_cool_images_Slice_x_tfromp_trim}
\caption{Example slice through 3-d dataset with \yt.}
\end{figure}
